\documentclass{article}
\usepackage{hyperref}
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}

\begin{document}
\begin{center}
    \thispagestyle{empty}
    \large \textbf{Yuling (Daniel) Shi\\}
    \normalsize Email: shiyuling@163.sufe.edu.cn $\mid$ Mobie: (86) 187-7023-2576 $\mid$ \href{yerbapage.github.io}{Website: yerbapage.github.io}   \\
    Address: No.777 Guoding Road, Yangpu District, Shanghai, P.R.China 200433\\
    \hrulefill
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \noindent \textbf{\underline{OBJECTIVE}} \\
% \noindent Graduate student looking for domain positions starting month and year. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%/

% \noindent \textbf{\underline{CORE SKILLS}} \\
% Skill 1 (years of experience), Skill 2 (years of experience), Skill 3 (years of experience) \\
% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\noindent \textbf{Shanghai University of Finance and Economics} \hfill Shanghai, China \\
\textit{Department of Mathematics} \hfill Sept 2018 - Present
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {Undergraduate in Applied Mathematics (Elite Program), Major GPA: \textbf{3.64/4(87.6/100)},
          Courses on AI: \textbf{Natural Language Processing (4.0), Deeping Learning (4.0), Machine Learning (3.7).}}
    \item {Scholarships: People's Scholarship, Outperforming Individual Scholarship \textbf{(2 out of 86)}, Featured Student \textbf{(2 out of 86)}.}
    \item {Solid expertise in: Python (Deep Learning, Scientific Computing), MATLAB, Bash, \LaTeX, Git; experienced in: C, C\texttt{++}, CMake, Javascript, SQL.\\}
          % FORTAN CUDA maybe
    % \item {Team working: Caption of school table tennis team, president of school table tennis club.\\}
          % \item {Solid expertise in: Python (Pytorch, Tensorflow, FEM), MATLAB, Bash, \LaTeX, Git; experienced in: C, C\texttt{++}, CMake, Javascript, SQL, SPSS\\} % FORTAN CUDA maybe
\end{itemize}

% \textbf{University name} \hfill City, State \\
% \textit{Degree name + Specialization} \hfill GPA: x.x/x.x \hfill month-year \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies.
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{PUBLICATIONS}} \\
\noindent [1] Xuehai Huang, \textbf{Yuling Shi}, Wenqing Wang:
A Morley-Wang-Xu element method for a fourth order elliptic singular perturbation problem. (\textit{Journal of Scientific Computing}, accepted) \\ % arXiv:2011.14064

% \noindent \textbf{Company name} \hfill City Name, State \\
% \textit{Role name} \hfill Month, Year $-$ Month, Year
% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
% \item {Developed XYZ using XYZ that led to X\% improvement.}
% \item {... \\}
% \end{itemize}

% \noindent \textbf{Competition Name} \hfill City Name, State \\
% \textit{Role name, Team name} \hfill Month, Year $-$ Month, Year
% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
% \item {Developed XYZ using XYZ that led to X\% improvement.}
% \item {Came in the top 10 OR received the most innovative award.}
% \item {... \\}
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{RESEARCH EXPERIENCE}} \\
\noindent \textbf{Research Assistant, Interpreting Predictions of NLP Models} \hfill Shanghai, China
\\ \textit{Advisor: Dr. Wanyun Cui} \hfill  Jan 2021 - Present
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {Studied recent conference tutorials and papers on interpretation techniques like SHAP, LIME and so on.} % integrated gradient.}
    \item {Analyzed changes in gradients of important words during the training process with Pytorch.}
    \item {Researched on interpreting how the model learned relations between words from the aspect of Taylor expansion.\\}
\end{itemize}

\noindent \textbf{Research Assistant, Robust Finite Element Method for A Singular Perturbation Problem} \hfill Shanghai, China
\\ \textit{Advisor: Prof. Xuehai Huang} \hfill Jul 2020 - Feb 2021
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {Studied scientific computing packages scikit-fem in Python and iFEM in MATLAB for finite element method. Contributed codes and reported bug for scikit-fem.}
    \item {Implemented a robust AMG-CG solver with designed preconditioner for decoupled equation. Achieved optimal convergence rate with Nitche's technique in the case of the boundary
    layers.}
    \item {Discovered and analyzed the super-convergence benefit from a simply modified right hand side.}
    % \item {Contributed codes and reported bug for the open source package scikit-fem when implementing experiments.}
    % \item {Analyzed and summarized experiment results in paper: A Morley-Wang-Xu element method for a fourth order elliptic singular perturbation problem (accepted by \textit{Journal of Scientific Computing}). \\}
    \item {Final paper has been accepted by \textit{Journal of Scientific Computing}. \\}
\end{itemize}

\noindent \textbf{Principal Investigator, Building Domain Knowledge Graph with Deep Learning Models}  \hfill Shanghai, China
\\ \textit{Advisor: Prof. Xuehai Huang} \hfill  Mar 2020 - Dec 2020
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {Applied NLP models to build a financial knowledge graph, studied models for named entity recognition, relation extraction and event extraction.}
    \item {Collected data with Scarpy, stored the data in Neo4j graph database and wrapped them up with Flask framework.}
    \item {Added labels to original sentences and included a BiGRU layer after BERT to improve the performance in named entity recognition task, implemented with Pytorch.}
    \item {Awarded as the "Excellent Project" in school and selected for oral presentation \textbf{(3 out of 165)}.\\}
\end{itemize}

\noindent \textbf{Project Leader, Kaggle Question Answering Competition} \hfill Shanghai, China
\\ \textit{Advisor: Ass.Prof. Hui Fang} \hfill Feb 2020 - Jun 2020
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {Ensembled models and improved training process by studying research papers to improve performance of BERT and similar models in question answering task.}
    \item {Outperformed the best submission in Kaggle leaderboard with smaller models. Implemented experiments in Pytorch including: pre-training on similar dataset, hard negative mining, adding special token, mixed precision training.}
    \item {Reached a final GPA of 4.0 in second year among juniors from Elite Program in Department of Electrical Engineering.\\}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{ACITIVTIES AND HONORS}} \\
\noindent \textbf{$1^{st}$ Prize in Mathematical Contest in Modeling of SUFE (Ranked 2/70)} \hfill Apr 2020 $-$ Apr 2020
% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
%     \item {Adopted machine learning and optimization models to analyze effects and duration of online courses.\\}
% \end{itemize}

% \noindent \textbf{President of School Table Tennis Club (with 300\texttt{+} members)} \hfill Sept 2019 $-$ Aug 2020
% % \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
% %     \item {Held competitions within and between schools, led outing activities and managed regular activities of the club.\\}
% % \end{itemize}

\noindent \textbf{$1^{st}$ Prize in National Olympiad in Physics (Provincial Area, top 0.02\%)} \hfill Sept 2016 $-$ Sept 2017 \\
% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
%     % \item {Self-studied undergraduate and graduate courses in Physics during high-school with strong motivation and ability to learn.\\}
%     \item {Self-studied undergraduate and graduate courses in Physics, able to solve problems with strong Physics backgrounds.\\}
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{OTHER SKILLS}} \\
\noindent \textbf{Language:} English (TOFEL 102), Chinese (mother language) \\
\noindent \textbf{Team working:} President of School Table Tennis Club (with 300\texttt{+} members) \\
\noindent \textbf{Interests that make me optimistic:} Table tennis ($5^{th}$ place in Shanghai Doubles Championship, $3^{rd}$ place in Teams) \\

\end{document}
